---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# threemc_example

We've noticed that when running TMB, system memory is spiking during tape optimisation and we would like to understand why. Below is a plot of memory usage when running the model with a relatively large country (Ghana)

```{r ghanaPlot, echo = FALSE}
mem <- memprof::monitor_read("data/gha_memprof_results.csv.gz")
plot(mem)
```

The memory is spiking during tape optimisation which means we need to run on a machine with > 500GB of memory. These are the biggest cluster nodes we have available, meaning we're sitting on a huge amount of compute which we only really need for a small fraction of the model fit. If we were able to reduce the memory usage we could run more concurrent models. We're trying to understand

* Why does the memory spike like this?
* Can we predict the size of the memory spike from size in input data, number of parameters etc.
* Can we save out the optimised tape and then use this for multiple model fits? This could allow us to do the costly optimisation on a beefy node but then run the rest of the simulation on smaller nodes.

This repo contains an example of a smaller model fit which can be run with about 11GB of RAM but still shows the memory spike during optimisation.

## Prerequisites

`readr`, `sf`, `TMB` and `threemc` packages

Install threemc from github
```r
remotes::install_github("mrc-ide/threemc")
```

## Running

Run the script from the command line via `./script.R` (working directory must be this repo root)q

or from R as

```
source("threemc_fit.R")
shell_dat <- readr::read_csv("data/shell_data_lso.csv.gz")
areas <- sf::read_sf("data/areas.geojson")
mod <- readLines("src/threemc.cpp")
fit <- threemc_fit(shell_dat, areas, mod, silent = TRUE)
```

## Profile

Run with profile from [memprof](https://github.com/mrc-ide/memprof)

```{r}
source("threemc_fit.R")
# load shell dataset
shell_dat <- readr::read_csv("data/shell_data_lso.csv.gz")
# load shapefiles
areas <- sf::read_sf("data/areas.geojson")
# load text from C++ mod into R
mod <- readLines("src/threemc.cpp")
mem <- memprof::with_monitor(threemc_fit(shell_dat, areas, mod, silent = TRUE))
plot(mem)
```

