---
title: "Testing New Compilation Method"
author: "Paddy O'Toole"
date: "2023-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here, we would like to test that the following have not been significantly 
changed by taking on kaskr's suggestions on the choice of AD framework
used by `TMB::compile` (TMBad vs the default of CppAD): 
1. modelling results and 
2. time to fit.

Of course, we would also like to have seen a decrease in the memory spike 
experienced while fitting!

## Prelims 

```{r}
library(dplyr)
library(ggplot2)
library(microbenchmark)
```


```{r}
# load shell and areas datasets for Lesotho
shell_dat_lso <- readr::read_csv("data/shell_data_lso.csv.gz")
areas <- sf::read_sf("data/areas.geojson")
```

```{r}
# Source functions & load mod 
source("threemc_fit.R")
mod <- readLines("src/threemc.cpp")
```

## Fit Models

Compile our two models:
```{r, results = "hide", message = FALSE}
# `framework` is passed to `TMB::compile`
mod_cppad <- tmb_compile_and_load(mod, framework = "CppAD")
mod_tmbad <- tmb_compile_and_load(mod, framework = "TMBad")
```

Fit our models with `threemc`.
```{r, results = "hide", message = FALSE}
# fit model with CPPad
fit_cppad <-  memprof::with_monitor(threemc_fit(
  shell_dat_lso, areas, mod_cppad, silent = TRUE
))
# fit model with TMBad 
fit_tmbad <-  memprof::with_monitor(threemc_fit(
  shell_dat_lso, areas, mod_tmbad, silent = TRUE
))
```

## 0: Memory used

Inspect the memory used by both AD frameworks with `memeprof`:
```{r}
bind_rows(
  select(memprof:::used_memory_total_by_time(fit_cppad$memory_use), 
         used = used, 
         time),
  select(memprof:::used_memory_total_by_time(fit_tmbad$memory_use), 
         used = used,
         time), 
  .id = "indicator"
) %>% 
  mutate(
    used      = used / 1e6,
    indicator = ifelse(indicator == 1, "CppAD", "TMBad")
  ) %>% 
  ggplot(aes(x = time, y = used, colour = indicator)) + 
  geom_line() + 
  ggtitle("CppAD vs TMBad: Memory Used") + 
  xlab("Time (s)") + 
  ylab("System memory used (MB)") + 
  theme_bw()
```

It appears that the TMBad framework uses substantially less memory, and does 
not experience a memory "spike". However, it is concerning that it seems to 
take more than twice as long to fit. 

## 1. Results 

We can calculate quantiles from our sample values, and plot these, to compare 
results from both models:
```{r}
res_cppad <- fit_cppad$result
res_tmbad <- fit_tmbad$result

out_cppad <- threemc::compute_quantiles(
  shell_dat_lso, fit = res_cppad, area_lev = 1
)
out_tmbad <- threemc::compute_quantiles(
  shell_dat_lso, fit = res_tmbad, area_lev = 1
)
```

```{r}
out_joined <- bind_rows(out_cppad, out_tmbad, .id = "indicator") %>% 
  filter(year == max(.data$year)) %>% 
  mutate(indicator = ifelse(indicator == 1, "CppAD", "TMBad"))

plt_fun <- function(out_joined, y_var) {
  
 out_joined %>% 
  ggplot(aes(
    x      = circ_age,
    # y      = cum_incM,
    y      = .data[[paste0(y_var, "M")]],
    ymin   = .data[[paste0(y_var, "L")]],
    ymax   = .data[[paste0(y_var, "U")]],
    group  = as.factor(indicator), 
    colour = as.factor(indicator)
  )) + 
  geom_ribbon(
    fill = "lightgrey",
    colour = NA
  ) +
  geom_line(size = 1) +
  scale_y_continuous(breaks = seq(0, 1, by = 1), labels = scales::label_percent(accuracy = 1)) +
  labs(
    x = "Age", y = "Coverage", colour = ""
  ) +
  theme_bw() +
  facet_grid(area_name ~ indicator) + 
  theme(
    
    panel.spacing = unit(6.5, "points"),
    strip.text.y = element_blank(), 
    strip.background.y = element_blank()
  ) 
}

cols <- c("cum_inc", "cum_inc_mmc", "cum_inc_tmc")
titles <- paste(
  c("Total", "Medical", "Traditional"), "Circumcision vs Age, 2021"
)

lapply(seq_along(cols), function(i) {
  plt_fun(out_joined, cols[i]) + 
    ggtitle(titles[i])
})
```

We can see that the two frameworks give what are essentially the same results. 

TODO: Add something on euclidean distance between quantile estimates

## 2. Time 

```{r, message = FALSE, results = "hide", warning = FALSE}
bm_res <- microbenchmark(
  "CppAD" = threemc_fit(
  shell_dat_lso, areas, mod_cppad, silent = TRUE
  ), 
  "TMBad" = threemc_fit(
  shell_dat_lso, areas, mod_tmbad, silent = TRUE
  ), 
  times = 5
)
```
```{r}
bm_res
```

```{r, include = FALSE}
bm_res_df <- data.frame(bm_res)
means <- bm_res_df %>% 
  group_by(expr) %>% 
  summarise(mean(time)) %>% 
  pull()
```

Therefore, CppAD is, on average, 
~`r round(means[2] / means[1], digits = 1)` 
times faster than TMBad. 

It is unclear how this scales up for larger countries. To simulate this, model
Lesotho at the country level: 
```{r, message = FALSE, results = "hide", warning = FALSE}
shell_dat_partial <- shell_dat_lso %>% 
    filter(area_level == 1) %>% 
    mutate(across(N:icens, ~ . * population)) %>% 
    group_by(year, circ_age, time, age) %>% 
    summarise(across(population:icens, sum), .groups = "drop") %>% 
    mutate(
        across(N:icens, ~ . / population), 
        area_id    = "LSO", 
        space      = 1, 
        area_level = 0
    ) %>% 
  relocate(area_id, space, area_level)
areas_partial <- filter(areas, area_level == 0)

bm_res_small <- microbenchmark(
  "CppAD" = threemc_fit(
  shell_dat_partial, areas, mod_cppad, silent = TRUE
  ), 
  "TMBad" = threemc_fit(
  shell_dat_partial, areas, mod_tmbad, silent = TRUE
  ), 
  times = 5
)
```
```{r}
bm_res_small
```

```{r, include = FALSE}
bm_res_small_df <- data.frame(bm_res_small)
means_small <- bm_res_small_df %>% 
  group_by(expr) %>% 
  summarise(mean(time)) %>% 
  pull()
```

Therefore, CppAD is, on average, 
~`r round(means_small[2] / means_small[1], digits = 1)` times
faster than TMBad at the country level (i.e. for a much smaller number 
of parameters), so unfortunately the difference in fit time for the two 
different AD schemes appears to increase with the need to estimate more 
parameters. This may cause our model with a time TMC effect to be very slow. It
would probably therefore be a good idea to make the choice of framework an 
option in `threemc`, whereby the user can choose to prioritise computational 
or time efficiency. 
